Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-04 manuscript.tex
update to kperf and small manuscript

The power spectrum uses the full magnitude of the {\bf k}-vector, which is set by the antenna baselines and bandwidths.  Note that largest bandwidth (which determines the smallest $\kpar$) is about 10 MHz, for larger bandwidths cosmic evolution begins to impact the result.  Figure \ref{fig:kperf} shows the allowed k-values based on the beamwidth/baseline (gray plus dark-blue overlap regions, the black lines are the limits) and a bandwidth of 10 MHz with 1024 channels (the blue and dark-blue overlap regions, the blue line is the lower limit).  The red-dashed line is the allowed smallest $k$-value attainable with this technique.  Note that at these red-shifts it is dominated by the bandwidth.

>>>>

The power spectrum uses the full magnitude of the {\bf k}-vector, which is set by the antenna baselines and bandwidths, as discussed above.  Note that cosmic evolution limits the largest bandwidth (which determines the smallest $\kpar$) to about 10 MHz -- for larger bandwidths the evolution of the Universe begins to impact the result.  For HERA, wavenumbers are dominated by the bandwidth, not the baseline.

Figure \ref{fig:kperf} is a rather busy plot showing many of the dependencies on wavenumber of bandwidth, configuration and the cosmos.  It shows the perpendicular, parallel and total resolution wavenumber as a function of redshift for various bandwidths and baselines.  The term {\em resolution} wavenumber is used, since it is a lower limit for that parameter since larger wavenumbers may be obtained at smaller bandwidths.  Blue lines denote $\kpar$ values, black lines denote $\kvpr$, and green lines denote total magnitude ($|{\bf k}|$) and the lines are labelled for the assumed bandwidth and/or baseline, depending on the type of wavenumber.  Obviously nearly any values may be used, but here a small sampling of values appropriate for HERA are used and the redshift range is appropriate for the extended frequency range that is the goal for HERA.  Also, by the $\kpar$ lines the additional ranges indicated by the horizontal lines centered at z=6,12, and 18 are the corresponding redshift extent for that bandwidth at those redshifts.  Note that for 100 MHz, the concept of a power spectrum at a given redshift is not defined, so some evolutionary model would have to be assumed (this is why the line is dashed and only the z=12 range is shown).
Also in Fig. \ref{fig:kperf}, the lime-green shaded region indicates a plausible region in which HERA could make the measurement and the lighter square within that region is the area that is being targeted in the first instance.
